### 2022-01-12 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@b54934cfcadbcbed63871af5a22f9b3a617069ac 🚀

\begin{longtable}[]{@{}lll@{}}
\toprule
Method & Embedding approach & Reference\tabularnewline
\midrule
\endhead
DeepWalk & graph walk & Perozzi et al. (2014)\tabularnewline
FastEmbed & graph through PCA/SVD analogue & Ramasamy \& Madhow
(2015)\tabularnewline
LINE & nodes through statistical divergence & Tang et al.
(2015)\tabularnewline
SDNE & nodes through auto-encoding & Wang et al. (2016)\tabularnewline
node2vec & node embedding & Grover \& Leskovec (2016)\tabularnewline
graph2vec & sub-graph embedding & Narayanan et al. (2017)\tabularnewline
HARP & nodes through a meta-strategy & Chen et al. (2017)\tabularnewline
\bottomrule
\end{longtable}

@@

@@

@@

>>>>

\begin{longtable}[]{@{}lll@{}}
\toprule
Method & Embedding approach & Reference\tabularnewline
\midrule
\endhead
RDPG & graphs through SVD & Young \& Scheinerman (2007)\tabularnewline
tSNE & nodes through statistical divergence & Hinton \& Roweis
(2002)\tabularnewline
DeepWalk & graph walk & Perozzi et al. (2014)\tabularnewline
FastEmbed & graph through PCA/SVD analogue & Ramasamy \& Madhow
(2015)\tabularnewline
LINE & nodes through statistical divergence & Tang et al.
(2015)\tabularnewline
SDNE & nodes through auto-encoding & D. Wang et al.
(2016)\tabularnewline
node2vec & node embedding & Grover \& Leskovec (2016)\tabularnewline
graph2vec & sub-graph embedding & Narayanan et al. (2017)\tabularnewline
HARP & nodes through a meta-strategy & Chen et al. (2017)\tabularnewline
Joint methods & multiple graphs & S. Wang et al. (2021)\tabularnewline
\bottomrule
\end{longtable}

@@

\leavevmode\hypertarget{ref-Hinton2002StoNei}{}%
Hinton, G., \& Roweis, S. T. (2002). Stochastic neighbor embedding.
\emph{NIPS}, \emph{15}, 833--840.

@@

\leavevmode\hypertarget{ref-Wang2021JoiEmb}{}%
Wang, S., Arroyo, J., Vogelstein, J. T., \& Priebe, C. E. (2021). Joint
Embedding of Graphs. \emph{IEEE Transactions on Pattern Analysis and
Machine Intelligence}, \emph{43}(4), 1324--1336.
\url{https://doi.org/10.1109/TPAMI.2019.2948619}

@@

\leavevmode\hypertarget{ref-Young2007RanDot}{}%
Young, S. J., \& Scheinerman, E. R. (2007). Random Dot Product Graph
Models for Social Networks. In A. Bonato \& F. R. K. Chung (Eds.),
\emph{Algorithms and Models for the Web-Graph} (pp. 138--149). Springer.
\url{https://doi.org/10.1007/978-3-540-77004-6_11}
